---
title: "accel_metrics_2021_Fuller"
author: "Daniel Fuller"
date: "22/02/2021"
output:
  html_document: 
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required packages
```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(naniar)
library(ggmap)
library(ggthemes)
library(sf)
library(rgeos)
library(cancensus)
library(cowplot)
library(ggspatial)
library(knitr)
library(corrr)

setwd("/Users/dfuller/Dropbox/Projects/INTERACT_github/publications/accel_metrics_2021_Fuller")
```

## Analysis Plan 

1. Health Survey wrangling
2. Accelerometer Metrics 
3. Accel Metrics + Health Survey
    * Physical activity (self-report)
    * Happiness
    * Social connectedness 

### Read in health data

```{r}
data <- read_csv("/Users/dfuller/Documents/INTERACT/data/health_clean.csv")

data <- data %>% select(interact_id, city_id, date_of_survey, gwb_happiness, belonging, belonging_cat, pwb_wellbeing, education_recode, age, gender_recode2, income_recode, leisure_modpa_freq, work_modpa_freq, work_vigpa_freq, leisure_vigpa_freq, sit_weekday, sit_weekend)
```

### Happiness

```{r}
summary(data$gwb_happiness)
table(data$gwb_happiness)
```

### Sense of community belonging

```{r}
table(data$city_id, data$belonging_cat)

ggplot(data, aes(belonging_cat)) + 
      geom_bar() + 
      facet_wrap(~ city_id)
```

### Read in accel metrics

```{r}
accel_metrics <- read_csv("/Users/dfuller/Documents/INTERACT/data/SaskatoonW1_three_init_fit_results.csv")
```

### Join in accel metrics to health survey

```{r}
health_accel <- left_join(accel_metrics, data, by = "interact_id")
```

### Associations with self-report activity

```{r}
### Self report data has a -7 for NA values 

health_accel <- health_accel %>%
          mutate(across(where(is.numeric), ~na_if(., -7)))

### Creating a mod+vig variable

health_accel$all_mod_vig_freq <- health_accel$leisure_modpa_freq + health_accel$leisure_vigpa_freq +                                  health_accel$work_modpa_freq + health_accel$work_vigpa_freq

### Summary stats on Mod Vig variable

summary(health_accel$all_mod_vig_freq)

mod_vig_pa_histo <- ggplot(health_accel, aes(all_mod_vig_freq)) + 
                geom_histogram()
plot(mod_vig_pa_histo)
```

### Associations with self-report sedentary time

```{r}
### Weekdays
summary(health_accel$sit_weekday)

sit_weekday_histo <- ggplot(health_accel, aes(sit_weekday)) + 
                geom_histogram()
plot(sit_weekday_histo)

### Weekend days
summary(health_accel$sit_weekend)

sit_weekend_histo <- ggplot(health_accel, aes(sit_weekend)) + 
                geom_histogram()
plot(sit_weekend_histo)
```

### Correlations

```{r}
x <- health_accel %>%
       select(all_mod_vig_freq, sit_weekday, sit_weekend, x1, x2, x3, x4, m1, m2, m3, a1, a2, a2) %>%
       correlate() %>%    # Create correlation data frame (cor_df)
       rearrange() %>%  # rearrange by correlations
       shave() # Shave off the upper triangle for a clean result

fashion(x)
```

### Correlation plot
```{r}
health_accel %>% 
  select(all_mod_vig_freq, sit_weekday, sit_weekend, x1, x2, x3, x4, m1, m2, m3, a1, a2, a2) %>%
  correlate() %>% 
  network_plot(min_cor = .2)
```

# Physical Activity

### Reading in the physical activity data from SenseDoc
```{}
data_temp <- NULL

data_temp <- dir(path = "/Users/dfuller/Documents/INTERACT/data/sensors/", full.names = TRUE, pattern = "*_sd.csv", recursive = TRUE) %>%
   purrr::map(function(i){
     dfhx <- read.csv(i, header = TRUE)
     temp <- bind_rows(data_temp, dfhx)
   })

sd_data <- bind_rows(data_temp)
rm(data_temp)
table(sd_data$city)
```
